\begin{thebibliography}{00}

% \bibitem{poz:diffgeom} Позняк Э.Г., Шикин Е.В.
% \emph{Дифференциальная геометрия: первое знакомство}. Москва, изд-во МГУ, 1990.


\bibitem{DLB} Ian Goodfellow and Yoshua Bengio and Aaron Courville
\emph{Deep Learning} MIT Press, 2016


\bibitem{deng-yu} Deng, L.; Yu, D. 
\emph{Deep Learning: Methods and Applications}
// Foundations and Trends in Signal Processing, 2014 1-199

\bibitem{peng-3d} Peng, Xingchao; Sun, Baochen; Ali, Karim; Saenko, Kate Saenko
\emph{Learning Deep Object Detectors from 3D Models} University of Massachusetts Lowell, 2015

\bibitem{Shrivastava-gap-real} Shrivastava, Ashish; Pfister, Tomas; Tuzel, Oncel; Susskind, Josh; Wang, Wenda; Webb, Russ 
\emph{Learning from Simulated and Unsupervised Images through Adversarial Training} arxiv.org, 2017

\bibitem{sanchez-at-glance} Sanchez, Cassie
\emph{At a Glance: Generative Models \& Synthetic Data} September 2017.

\bibitem{gan-1} Ian J. Goodfellow, Jean Pouget-Abadie, Mehdi Mirza, Bing Xu, David Warde-Farley, Sherjil Ozair, Aaron Courville, Yoshua Bengio
\emph{Generative Adversarial Networks} 2014

\bibitem{kumar} Y. Kumar, R. Janardan, and B. Larson, 
\emph{Automatic feature identification in dental meshes} Computer-Aided Design and Applications, vol. 9, no. 6, pp. 747–769, 2012.

\bibitem{gan-super} Christian Ledig, Lucas Theis, Ferenc Huszar, Jose Caballero, Andrew Cunningham, Alejandro Acosta, Andrew Aitken, Alykhan Tejani, Johannes Totz, Zehan Wang, Wenzhe Shi
\emph{Photo-Realistic Single Image Super-Resolution Using a Generative Adversarial Network} 2017

\bibitem{pu-net} Lequan Yu, Xianzhi Li, Chi-Wing Fu, Daniel Cohen-Or, Pheng-Ann Heng
\emph{PU-Net: Point Cloud Upsampling Network} The Chinese University of Hong Kong, Tel Aviv University, Shenzhen Institutes of Advanced Technology, Chinese Academy of Sciences, 2018

\bibitem{point-grid} Truc Le, Ye Duan
\emph{PointGrid: A Deep Network for 3D Shape Understanding} University of Missouri, 2018

\bibitem{point-net-plus} Charles R. Qi Li Yi Hao Su Leonidas J. Guibas
\emph{PointNet++: Deep Hierarchical Feature Learning on Point Sets in a Metric Space} Stanford University, 2017

\bibitem{octree-based} Peng-Shuai Wang, Yang Liu, Yu-Xiao Guo, Chun-Yu Sun, Xin Tong
\emph{O-CNN: Octree-based Convolutional Neural Networks for 3D Shape Analysis} 2017

\bibitem{spherical-conv-1} Huan Lei, Naveed Akhtar, Ajmal Mian
\emph{Spherical Convolutional Neural Network for 3D Point Clouds} University of Western Australia, 2018

\bibitem{spherical-cnn} Taco S. Cohen, Mario Geiger, Jonas Köhler, Max Welling
\emph{SPHERICAL CNNS} University of Amsterdam, 2018

\bibitem{3d-gan} Jiajun Wu, Chengkai Zhang, Tianfan Xue, William T. Freeman, Joshua B. Tenenbaum
\emph{Learning a Probabilistic Latent Space of Object Shapes via 3D Generative-Adversarial Modeling} 2017

\bibitem{3d-autoencoder} Andrew Brock, Theodore Lim, J.M. Ritchie, Nick Weston
\emph{Generative and Discriminative Voxel Modeling with Convolutional Neural Networks} 2016

\bibitem{adversarial-autoencoder} Maciej Zamorski, Maciej Zieba, Rafal Nowak, Wojciech Stokowiec and Tomasz Trzcinski
\emph{Adversarial Autoencoders for Generating 3D Point Cloud} 2018

\bibitem{seg-cloud} Lyne P. Tchapmi, Christopher B. Choy, Iro Armeni, JunYoung Gwak, Silvio Savarese
\emph{SEGCloud: Semantic Segmentation of 3D Point Clouds} 2017

\bibitem{lrgm-cloud} Panos Achlioptas, Olga Diamanti, Ioannis Mitliagkas, and Leonidas J Guibas.
\emph{Learning Representations and Generative Models For 3D Point Clouds} Proceedings
of the 35th International Conference on Machine Learning 2018

\bibitem{metrics-source} Haoqiang Fan, Hao Su, Leonidas Guibas
\emph{A Point Set Generation Network for 3D Object Reconstruction from a Single Image} arXiv e-prints 2016

\bibitem{stat-shape-1} Alan Brunton, Augusto Salazar, Timo Bolkart, Stefanie Wuhrer
\emph{Statistical Shape Spaces for 3D Data: A Review} Chi Hau Chen. Handbook of Pattern Recognition and Computer Vision, 5th Edition, 2016, 978-981-4656-52-8. 

\bibitem{stat-shape-2} Alan Brunton, Augusto Salazar, Timo Bolkart, Stefanie Wuhrer
\emph{Review of Statistical Shape Spaces for 3D Data with Comparative Analysis for Human Faces}

\bibitem{bishop} Christopher M. Bishop
\emph{Pattern Recognition and Machine Learning} Information Science and Statistics, 2006


\bibitem{assignment-task-1} Хемди А. Таха.
\emph{Введение в исследование операций} 7-е издание. Пер. с англ. — М.: Издательский дом «Вильямс», 2005.

\bibitem{assignment-task-2} Вагнер Г.
\emph{Основы исследования операций} Пер. с англ. — М.: Издательство «Мир», 1972.. — Т. 1.

\bibitem{hungarian-alg} Harold W. Kuhn
\emph{Variants of the Hungarian method for assignment problems} Naval Research Logistics Quarterly, 3: 253—258, 1956

\bibitem{python:doc} Python v3.5 documentation
[HTML] (http://docs.python.org/3.5).

\bibitem{python:lutz} Лутц М.
\emph{Изучаем Python, 4-е издание.} – Пер. с англ. – СПб.: Символ-Плюс, 2011.

\bibitem{wahba} Wahba, G. 
\emph{Problem 65–1: A Least Squares Estimate of Spacecraft Attitude}, SIAM Review, 1965, 7(3), 409

\bibitem{procrustes-1}  Schönemann, P.H.
\emph{A generalized solution of the orthogonal Procrustes problem}, Psychometrika, 31, 1966

\bibitem{procrustes-2} Gower, J.C; Dijksterhuis, G.B.
\emph{Procrustes Problems}, Oxford University Press, 2004

\bibitem{icp-main} P.J. Besl, N.D. McKay.
\emph{A method for registration of 3D shapes} IEEE Transactions on Pattern Analysis and Machine Intellinegce 14 (1992) 239– 254.

\bibitem{icp-2} B. K. P. Horn.
\emph{Closed-form solution of absolute orientation using unit quaternions} J. Opt. Soc. Amer. Avol. 4, no. 4, pp. 629-642, Apr. 1987.

\bibitem{icp-non-min} Tsin, Yanghai; Kanade, Takeo.
\emph{A Correlation-Based Approach to Robust Point Set Registration} Computer Vision ECCV. Lecture Notes in Computer Science. 3023. Springer Berlin Heidelberg

\bibitem{icp-non-rigid} Shiyang Chenga, Ioannis Marrasa, Stefanos Zafeirioua, Maja Pantic.
\emph{Statistical non-rigid ICP algorithm and its application to 3D face alignment} Image and Vision Computing
Volume 58, February 2017, Pages 3-12


\end{thebibliography}